%!TEX program=xelatex
\documentclass[a4paper,12pt,utf8]{ctexbook}
\usepackage{titletoc}
\usepackage{titlesec}
\usepackage[a4paper,text={125mm,195mm},centering,left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{imakeidx}
\usepackage{multicol}
\usepackage[colorlinks,linkcolor=blue]{hyperref}
\usepackage{amsmath, amssymb, amsfonts, mathrsfs}
\usepackage{mathtools}

\DeclareFontFamily{U}{mathx}{\hyphenchar\font45}
\DeclareFontShape{U}{mathx}{m}{n}{<-> mathx10}{}
\DeclareSymbolFont{mathx}{U}{mathx}{m}{n}
\DeclareMathAccent{\widebar}{0}{mathx}{"73}

\usepackage{systeme}
%\usepackage{draftwatermark, everypage}
\usepackage{draftwatermark}
\SetWatermarkText{Version 0.3}
\SetWatermarkLightness{0.95}
\SetWatermarkScale{0.9}

\usepackage{graphicx}
\usepackage{subfig}
\usepackage{tikz,pgf}
\usepackage{color, xcolor}
\usepackage{pgfplots}
\pgfplotsset{compat=1.16}

\usepackage{makecell}
\usepackage{float}
%On Linux
%\setmainfont{DejaVu Sans}
\setCJKmainfont{Noto Serif CJK SC}
\setCJKsansfont{Noto Sans CJK SC}
%On Windows
%\setmainfont{Times New Roman}
%\setCJKmainfont{宋体}
%\setCJKsansfont{黑体}

\makeindex
\bibliographystyle{plain}

%\abovedisplayshortskip=0pt
%\belowdisplayshortskip=0pt
%\abovedisplayskip=0pt
%\belowdisplayskip=0pt
%\setlength{\abovecaptionskip}{-0.1cm}
%\setlength{\belowcaptionskip}{-0.2cm}

\graphicspath{{img/}}

\titlecontents{chapter}[4em]{\bf \large \vspace{10pt}}{\contentslabel[\color{blue}\thecontentslabel]{4em}}{\hspace*{-4em}}{}

\makeatletter
\renewcommand{\cleardoublepage}{\relax
  \clearpage
  \if@twoside \ifodd\c@page\relax\else
  \thispagestyle{empty}%
  \tikz[remember picture, overlay] \node  at (current page.center)
{\zihao{2} 本\ 页\ 刻\ 意\ 留\ 白};\newpage\fi\fi}
\makeatother


\begin{document}
\title{\bf \zihao{0} 计\ 算\ 水\ 力\ 学\ 讲\ 义}
\author{李\ 丹}
\date{二〇二二年四月}
\frontmatter
\maketitle
\thispagestyle{empty}

\include{preface}
\clearpage

\pagenumbering{roman}
\pagestyle{plain}
%%\setcounter{page}{1}
\tableofcontents
\newpage

\mainmatter

\pagenumbering{arabic}
\pagestyle{headings}

\setlength{\lineskip}{0.5em}
\setlength{\parskip}{0.5em}
\include{ch01}
\cleardoublepage

\include{ch02}
\cleardoublepage

\include{ch03}
\cleardoublepage

\include{ch04}
\cleardoublepage

\include{ch05}
\cleardoublepage

\include{ch06}
\cleardoublepage

\begin{thebibliography}{1}
  \bibitem{ref1} 汪德爟. 计算水力学理论与应用. 北京：科学出版社, 2011
  \bibitem{ref2} John D. Anderson, Jr.. Computational Fluid Dynamics The Basics with
  Applications. Singapore: McGraw-Hill, Inc, 1995
  \bibitem{ref3} H K Versteeg, W Malalasekera. An Introduction to Computational
  Fluid Dynamics The Finite Volume Method. 北京：世界图书出版公司北京公司, 2010
  \bibitem{ref4} 陶文铨. 数值传热学. 西安：西安交通大学出版社, 2001
  \bibitem{ref5} 郑邦民, 赵昕. 计算水动力学. 武汉：武汉大学出版社, 2001
  \bibitem{ref6} Jameson, A., Schmidt, W., Turkel, E.. Numerical solutions of the
  Euler equations by finite volume methods using Runge-Kutta time-stepping
  schemes. American Institute of Aeronautics and Astronautics, Fluid and Plasma
  Dynamics Conf., Palo Alto CA, AIAA-81-1259, 1981.
  \bibitem{ref7} Garcia-Navarro, P., Alcrudo, F., Saviron, J. M.. 1-D
  open-channel flow simulation using TVD-McCormack scheme. Journal of Hydraulic
  Engineering, 1992, 118(10), 1359-1372.
\end{thebibliography}
\cleardoublepage


\end{document}

